Tropical Andes montane and lowland forest bird and mammal species GBIF

### 2023-10-17 code/L0/L0_TropicalAndes_frugivores_GBIF.Rmd
add subset to Tropical Andes habitat shape code, update object names

# Retrive GBIF download, save file, and load into r
```{r}
d <- occ_download_get("0129743-230530130749713", path = output_path, overwrite = TRUE) %>%
  occ_download_import()
```

# Summary 
```{r}
glimpse(d)
```

```{r}
print("The number of records is")
nrow(d)
print("The number of species is")
length(unique(d$species))
print("The number of families is")
length(unique(d$family))
```

# Extract species list
```{r}
GBIF_occ_SpeciesList <- unique(d$species)
```

# Write data to csv
```{r}
write.csv(d, file = file.path(output_path,"TropicalAndes_GBIF_frugivore_occ.csv"))

>>>>

# Retrive GBIF download, save file, and load into r
```{r}
d <- occ_download_get("0009771-231002084531237", path = output_path, overwrite = TRUE) %>%
  occ_download_import()
```

# Subset occurrence to Tropical Andes IUCN Montane and Lowland forest

## Read in Forest shape
```{r}
TropicalAndes_IUCNHabitat_Forest <- read_sf(file.path(data_path, "Forest_sf.shp"), layer = "Forest_sf")
```

## Convert data frame to sf object
```{r}
TropicalAndes_frugivore_occ <- st_as_sf(x = d, 
                        coords = c("decimalLongitude", "decimalLatitude"),
                        crs = "+proj=longlat +datum=WGS84 +no_defs")
```

# Crop occurrence data to forest extent
```{r}
TropicalAndes_frugivore_occ_forest <- TropicalAndes_frugivore_occ[Forest_sf,]
```

# Summary 
```{r}
glimpse(TropicalAndes_frugivore_occ_forest)
```

```{r}
print("The number of records is")
nrow(TropicalAndes_frugivore_occ_forest)
print("The number of species is")
length(unique(TropicalAndes_frugivore_occ_forest$species))
print("The number of genera is" )
length(unique(TropicalAndes_frugivore_occ_forest$genus))
print("The number of families is")
length(unique(TropicalAndes_frugivore_occ_forest$family))
```

# Extract species list
```{r}
GBIF_occ_SpeciesList <- unique(TropicalAndes_frugivore_occ_forest$species)
```

# Write data to csv
```{r}
write.csv(TropicalAndes_frugivore_occ_forest, file = file.path(output_path,"TropicalAndes_GBIF_frugivore_occ.csv"))
